---
title: cacodes
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# What it is

An R package to look up text from [CA Legislative Information](https://leginfo.legislature.ca.gov/)

## How to use it

Load using `library`:

```{r loadlibs}
library(cacodes)
```

Look up charge codes using `leg_info`:

```{r ex-sing-lookup}
leg_info("PC 22810(A)")
```

You can look up multiple codes:

```{r ex-multi, cache = TRUE}
codes <- c("PC 602", "VC 23153", "HS 11377(A)")    
leg_info(codes)
```

Using with `data.frame`s. `as.character` can take one or more `leg_info` responses and extract just the legislative text (which can then be passed on, e.g. to look for keywords or to summarize):

```{r ex-dataframe, message = FALSE, warning = FALSE, cache = TRUE}
library(dplyr)
charges <- data_frame(id = 1:3, charge = codes)
charges
charges %>%
    mutate(law = leg_info(charge),
           law_text = as.character(law))
```

## Installation

This package is still under development. The development version can be installed from GitHub using the [devtools pacakge](https://cran.r-project.org/package=devtools)

``` r
devtools::install_github("tarakc02/cacodes")
```
